---
title: "Chicken Feed"
author: "Evangela McGarity"
date: "03/03/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```
```{r include=FALSE}
require(tidyverse)
require(tigerstats)
mydata <- read.csv(file = "chickens.csv")
```

##  Chicken feed study  

data set has chicken weights and 4 variables:
  1.  chicken weight  
  2.  chicken feed type  
  3.  chicken time in the 40" run  
  4.  chicken sex   

Idea is to determine which of the variables affect chicken weight 
The weight and time to run are numerical variables, gender and feed type are categorical variables

So we'll use templatesRMD Cat Numerical, look for the section that has an 'aov'

```{r}
plot(weight~sex,data=mydata)
```
<!-- This question is like a bunch of t-tests, but instead of doing the t-test a bunch of times we use ANOVA to do all the comparisons at once!  !-->

### get the data


# Numerical results

```{r}
favstats(weight~sex,data=mydata)
```

# Inferential  
  
```{r}
t.test(weight~sex,data=mydata)
```
### We conclude that sex is not a significan factor in the weight of the chickens.

<!-- plot chicken weight against each of the three explanatory variables.  Weight against a categorial varable is a boxplot, weight against a numerical variable is a scatter plot !-->


### Lets look at speed.
###Plot scatterplot

```{r}
plot(weight~speed,data=mydata)
```

# Numerical results

```{r}
cor(weight~speed,data=mydata)
```
# Inferential  (Build linear model)
  
```{r}
model.1 <- lm(weight~speed,data=mydata)
summary.lm(model.1)
```
The conclusion is speed is not a useful variable to explain chicken weight.
###Plot boxplots

```{r}
plot(weight~feed,data=mydata)
```
   
```{r}
favstats(weight~feed,data=mydata)
```
# Inferential

```{r}
model1 <- aov(weight~feed,data=mydata)
summary.aov(model1)
```

```{r}
#we specify the margins starting at the bottom and proceeding clockwise - thus 8.7 is the left side margin to hold the names of the factors
par(mar = c(3, 8.7, 2, 2))
plot(TukeyHSD(model1),las=2)
```

# conclusion 
Neither sex or speed are any influence on chicken weight are important.
However feed is very important.